### 2016-08-02 P4-Explore-and-Summarize-Data/submission.Rmd
Update submission.Rmd

### Statistical summary of the variables in the dataset
```{r, summary}
summary(rw)
```
As we are primarily interested in quality of the red wines, let's see some basic statistics about it
```{r }
summary(rw$quality)
```
* We've found that the quality lies in the range of [3, 8] with mean is equal to 5.636.

@@

ggplot(data = rw, aes(x = rating)) +
  geom_bar()
```

### Calculate total acidity
To calculate sum of all acids in the red wines, we create new variable ```total.acidity```.

@@

ggplot(data = rw, aes(x = alcohol)) +
  geom_histogram() + 
  scale_x_log10() +
  xlab('alcohol (% volume')
```

@@

@@

### Plot One : Effect of alcohol on wine quality
```{r , Plot_One}
ggplot(data = rw, aes(quality, alcohol, fill = rating)) +
  geom_boxplot() +
  ggtitle('Alcohol Levels on Wine Quality') +
  xlab('Quality') +
  ylab('Alcohol (% volume)')

@@

### Plot Two : Effect of acids on wine quality
```{r , Plot_Two}
grid.arrange(ggplot(data = rw, aes(quality, fixed.acidity, fill = rating)) +
               geom_boxplot(),
             ggplot(data = rw, aes(quality, volatile.acidity, fill = rating)) +
               geom_boxplot(),
             ggplot(data = rw, aes(quality, citric.acid, fill = rating)) +
               geom_boxplot(),
             ncol = 2)
```

>>>>

### Statistical summary of the variables in the dataset
```{r, summary}
summary(rw)
```
As we are primarily interested in quality of the red wines, let's see some basic statistics about it
```{r }
summary(rw$quality)

ggplot(data = rw, aes(as.factor(quality), fill = quality)) +
  geom_bar() +
  theme_replace() +
  xlab("Quality")

* We've found that the quality lies in the range of [3, 8] with mean is equal to 5.636.

@@

ggplot(data = rw, aes(x = as.factor(rating), fill = rating)) +
  geom_bar() +
  theme_minimal() +
  scale_fill_brewer(type = 'seq', palette = 2)
```

Summary of the ```rating```:

```{r}
summary(rw$rating)
```

### Calculate total acidity
To calculate sum of all acids in the red wines, we create a new variable called ```total.acidity```.

@@

ggplot(data = rw, aes(x = alcohol)) +
  geom_histogram() + 
  scale_x_log10() +
  xlab('alcohol (% volume')

@@

Correlation between ```residual.sugar``` and ```chlorides``` :

```{r}
cor.test(rw$residual.sugar, rw$chlorides)
```

@@

### Plot One : Effect of alcohol on wine quality
```{r , Plot_One}
ggplot(data = rw, aes(as.factor(quality), alcohol, fill = rating)) +
  geom_boxplot() +
  ggtitle('Alcohol Levels on Wine Quality') +
  xlab('Quality') +
  ylab('Alcohol (% volume)') +
  scale_fill_brewer(type = 'seq', palette = 1)

@@

### Plot Two : Effect of acids on wine quality
```{r , Plot_Two}
grid.arrange(ggplot(data = rw, aes(as.factor(quality), fixed.acidity, fill = rating)) +
               geom_boxplot() +
               xlab("Quality") +
               ylab("Fixed Acidity (g / dm^3)") +
              scale_fill_brewer(type = 'seq', palette = 1),
             ggplot(data = rw, aes(as.factor(quality), volatile.acidity, fill = rating)) +
               geom_boxplot() +
               xlab("Quality") +
               ylab("Volatile Acidity (g / dm^3)") +
              scale_fill_brewer(type = 'seq', palette = 1),
             ggplot(data = rw, aes(as.factor(quality), citric.acid, fill = rating)) +
               geom_boxplot() +
               xlab("Quality") +
               ylab("Citric Acid (g / dm^3)") +
              scale_fill_brewer(type = 'seq', palette = 1),
             ncol = 1)
```
